---
title: "Homework 5"
author: Vera Xu
output: github_document
---

This is my solution to HW5.

```{r, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
  )

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
  )

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1 demo by Jeff in class

Read in the data.

```{r, message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r, message = FALSE, warning = FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r, message = FALSE, warning = FALSE}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  ) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2

##### Create a dataframe containing all file names for p2

```{r}
p2_list = 
  list.files("./data/p2_data")
```

#####  Iterate over file names and read in data for each subject

```{r, message = FALSE, warning = FALSE}
p2_load = function(file_list) 
  {
  path = str_c("./data/p2_data/", file_list)
  read_csv(path)
  }

p2_data = 
  purrr::map(p2_list, p2_load) %>%
  bind_rows() %>%
  mutate(file_name = p2_list)
```

#####  Tidy the result

```{r, message = FALSE, warning = FALSE}
p2_tidy_data = 
  p2_data %>%
  mutate(file_name = gsub(".csv", "", file_name)) %>%
  separate(file_name, into = c("trt_group", "id"), sep = "_") %>%
  pivot_longer(week_1:week_8, 
               names_to = "week",
               values_to = "value") %>%
  mutate(week = gsub("week_", "", week))
```

#####  Make a spaghetti plot showing observations on each subject over time

```{r}
p2_tidy_data %>%
  ggplot(aes(x=week, y=value, color=id, group = id)) + 
  geom_point() + 
  geom_line() +
  facet_grid(. ~ trt_group)
```

We can tell from the spaghetti plot above that the values of measurement in the control group is in general lower than the experiment group. The values of control group remained flat over the 8 weeks of follow-up, while the values of experiment group steadily increased over the 8 weeks of follow-up.


## Problem 3

##### Define function to generate sample dataset and perform ttest

```{r}
n = 30
sigma = 5

one_sample_ttest = function(mu, h_null) {
  
  sample_data = tibble(
    x = rnorm(n=30, mean = mu, sd = 5),
  )
  
  sample_data %>% 
    t.test(mu = h_null) %>%
    broom::tidy()
}


```

##### Set mu=0 and generate 5000 datasets from the model to perform ttest

```{r}
output_mu_0 = vector("list", 5000)

for (i in 1:5000) {
  output_mu_0[[i]] = one_sample_ttest(mu = 0, h_null = 0)
}

mu_0_results = bind_rows(output_mu_0)
```

```{r}
for (k in 1:6) {
  output_mu_[[i]] = one_sample_ttest(mu = k, h_null = 0)
}

mu_0_results = bind_rows(output_mu_0)
```

